---
title: "measured."
description: |
  A one-time trophy bitch screams into the void.
author: 
  - name: Charles T. Gray
    url: https://twitter.com/cantabile
    affiliation: R-Ladies
    affiliation_url: https://rladies.org/
site: radix::radix_website
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      # eval = FALSE, 
                      cache = FALSE)
```

What if one practices mathematical science like music?

My goal is to spend four hours a day on *work with intent*[^1].

For a sanity, efficiency, and inspiration, I intend to balance my time between three categories: 

- research, $\Phi$; 
- skills, $\theta$; and 
- administrative tasks, $\psi$.


## load packages and get data

```{r}
# packages
library(tidyverse)
library(googlesheets)
library(lubridate)
library(latex2exp)

```

See [repo](https://github.com/softloud/measured/blob/master/index.Rmd) for data import script.

```{r import, echo=FALSE, eval=TRUE}
# import

# import time tracker data (exported manually from iphone app atracker)
time_tracker_raw <- read_csv("~/Downloads/Details-20170101-20190228.csv")

# import measures (googlesheet where I track things manually)
measures <- gs_title("measures")

 
```


```{r packages and data, echo=FALSE, message=FALSE}

# daily totals
time_tracker <- time_tracker_raw %>%
  # tidy column names
  rename(
    task = `Task name`,
    description = `Task description`,
    start = `Start time`,
    finish = `End time`,
    duration = Duration,
    duration_hrs = `Duration in hours`,
    note = Note,
    category = Category
  ) %>%
  mutate(
    # get date object, as I'll want to do things by day
    start = dmy_hm(start),
    finish = dmy_hm(finish),
    date = date(start),
    month = month(start)
  ) %>%
  filter(category != "wellness") %>%
  select(-note, -description) %>%
  group_by(date, category) %>%
  summarise(hrs = sum(duration_hrs)) %>%
  mutate(month = month(date, label = TRUE, abbr = FALSE),
         year = year(date))



# extract daily record
daily <- measures %>%
  gs_read(ws = "daily_record") %>%
  mutate(date = ymd(date))
operations <- measures %>%
  gs_read(ws = "operations") %>%
  mutate(initiated = ymd(initiated))

# workload definitions
workload_key <- measures %>%
  gs_read(ws = "workload") %>%
  select(-phi, -theta, -psi, -exercise) %>%
  gather(key = "category", value = "hrs_goal", -workload) %>%
  separate(category, into = "category", sep = "_")


```

## how have I done over the last 100 days? 

```{r workload achieved}
century <- time_tracker %>%
  filter(date >= (today() - 100)) %>%
  left_join(workload_key, by = "category")




```


## practice routine

Aim for one or two hardcore days, two or three moderate, and one or two light days[^2]. 

```{r geom parameters}


# little miss fussy plot parameters

alpha = 0.4
colour = "darkgrey"
fill = "black"

```


### workload achieved

```{r labelling ggplots}
category_labels <- c(
  "phi" = "phi",
  "psi" = "b",
  "theta" = "c")


```


I want these to be nice and pointy around the dotted line.

```{r}
time_tracker %>%
  filter(date >= today() - 99) %>% 
  mutate(category = if_else(category == "phi", "Phi", category)) %>% 
  ggplot(aes(x = hrs)) +
  geom_vline(linetype = "dotted", xintercept = 4 / 3) +
  geom_density(alpha 
               = alpha,
               colour = colour,
               fill = fill) +
  facet_grid( ~ category, scales = "free", labeller = label_parsed) 
  
```



## monthly distributions 

```{r}


# 2018
time_tracker %>%
  filter(year == 2018, month(date) > 7) %>%
  ggplot(aes(x = hrs)) +
  geom_vline(linetype = "dotted", xintercept = 4 / 3) +
  geom_density(alpha = alpha,
               colour = colour,
               fill = fill) +
  facet_grid(category ~ month, scales = "free", 
             labeller = label_parsed) +
  labs(title = "2018",
       caption = "test")

# 2019
time_tracker %>%
  filter(year == 2019) %>%
  ggplot(aes(x = hrs)) +
  geom_vline(linetype = "dotted", xintercept = 4 / 3) +
  geom_density(alpha = alpha,
               colour = colour,
               fill = fill) +
  facet_grid(category ~ month, scales = "free", labeller = label_parsed) +
  labs(title = "2019",
       caption = "")

```


## my system

I use a combination of gtd, pomodoros, and bullet journaling in my productivity system.

And a toy elephant, along with a [digraph](https://en.wikipedia.org/wiki/Directed_graph).

***

*Work in progress.*

[^1]: This term is adopted from a piano teacher that I studied under, that I subsequently adapted into my own teaching. She encouraged me to *practice with intent*; that is, play what you intend to play. I found this to be particularly useful for discouraging my students, and myself, from the age-old pitfall of playing a piece of music until you make a mistake and stopping and playing that section over until you get it right. It's better to play *through* the piece, which empowers you to adapt to mistakes you will inevitably play and, most importantly, not lose time. Oddly, it appeared to be a universal misconception, myself included, that without careful consideration, the attempt to *get the notes right* inevitably means the **rhythm is wrong**, and thus you get nothing right after all. Best, therefore, to play through the piece.    


[^2]: I would tell my piano students to have a sense of a what light day is, what a moderate workload, and what a hardcore day looks like. If I get locked in with the impression that a hardcore workload day is the norm, then I get deflated and start avoiding doing work altogether. It feels insurmountable. Instead, I would advise them to expect days where you don't want to do anything at all. I recently experienced this. I discovered I was not meeting my defintion of a light workload (12 poms). I now realise that waas too ambitious. I was missing entire days of work. I redefined my light workload as a moderate workload, and am now hitting hardcore goals some days. 
