---
title: "measured."
description: |
  A one-time trophy bitch screams into the void.
site: radix::radix_website
---

My newfound role as a math-talking-doing-advocate grrl is an experiment. What if one practices science like music?

My goal is to spend four hours a day on deep work.

```{r get data, echo=TRUE}
# packages
library(tidyverse)

# get data
tracker_data <- readr::read_csv("atracker-data-2018-11-12.csv") %>%
  # tidy up columns
  rename(start = `Start time`,
         end = `End time`,
         duration = Duration,
         hours = `Duration in hours`,
         category = Category,
         project = `Task name`) %>%
  # drop things unused features
  select(-`Task description`, -Note) %>% 
  # convert dates to date objects in R
  mutate(start = lubridate::dmy_hm(start),
         end = lubridate::dmy_hm(end),
         duration = lubridate::as.duration(duration),
         day = lubridate::day(start),
         month = lubridate::month(start, label = TRUE),
         date = lubridate::date(start))



```

## distribution of deep work hours each day by month

```{r echo=TRUE}
# plot monthly distributions
tracker_data %>% 
  filter(category != "Wellness") %>%  # for now, need to join in calendar and munge yoga
  group_by(date, month) %>% 
  summarise(time = sum(duration) / 3600) %>%
  ggplot(aes(x = time)) +
  geom_histogram(bins = 10) +
  facet_grid(month ~ .)

```

## distribution of deep work hours by month and category


```{r echo=TRUE}
# plot monthly by category distributions
tracker_data %>% 
  group_by(date, category, month) %>% 
  summarise(time = sum(duration) / 3600) %>%
  filter(category != "Wellness") %>%  # for now, need to join in calendar and munge yoga
  ggplot(aes(x = time)) +
  geom_histogram(bins = 10) +
  facet_grid(month ~ category)

```


## How is my focus tracking over time? 


```{r echo=TRUE}
# plot monthly by category distributions
tracker_data %>% 
  filter(category != "Wellness") %>%  # for now, need to join in calendar and munge yoga
  group_by(day, month) %>% 
  summarise(time = sum(duration) / 3600) %>% 
  ggplot(aes(x = day, y = time)) +
  geom_line(alpha = 0.7) +
  geom_point(alpha = 0.5) +
  geom_hline(yintercept = 4, linetype = "dotted") +
  facet_grid(month ~ .)

# with categories
tracker_data %>% 
  filter(category != "Wellness") %>%  # for now, need to join in calendar and munge yoga
  group_by(day, month, category) %>% 
  summarise(time = sum(duration) / 3600) %>% 
  ggplot(aes(x = day, y = time)) +
  geom_line(alpha = 0.7) +
  geom_point(alpha = 0.5) +
  geom_hline(yintercept = 4, linetype = "dotted") +
  facet_grid(month ~ category)

```


## my system

I use a combination of gtd, pomodoros, and bullet journaling in my productivity system.

And a toy elephant, along with a [digraph](https://en.wikipedia.org/wiki/Directed_graph).


***

*Work in progress.*
