---
title: "wrangling errors"
description: |
  filtering a list by type
author:
  - name: Charles T. Gray
    url: https://twitter.com/cantabile
date: 02-19-2019
output:
  radix::radix_article:
    self_contained: false
categories:
  - wrangling
  - error handling
  - debugging
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r packages}
# packages used in this post
library(tidyverse)
```

I want to wrangle some errors out of the results of a function. 

At the moment, my function returns `NULL` if a warning or an error is thrown, which gets me the results that ran, but I'd like to have more information about the trials that didn't run. 

I think I can get my function to return a dataframe of results if the function works as intended, and a character string detailing the error or warning if the function fails. This will give me a list of dataframes intermixed with character strings. 

So, my question of the day is **how to filter a list by type**?

First, I'll create a dummy list[^1].

```{r dummy data}
# create a list of dataframes and character strings
playlist <- list(
  "Beanie 'Legs' McGraw",
  "Peug the Door-opening Cat",
  iris %>% select(Sepal.Length, Species) %>%  filter(Species == "setosa") %>% head(),
  iris %>% select(Sepal.Length, Species) %>% filter(Species == "versicolor") %>% head(),
  iris %>% select(Sepal.Length, Species) %>% filter(Species == "virginica") %>% head(),
  "Lord Euclid of the Fluffy Butt"
)

playlist %>% str()
```

So, how do I get the dataframes out into one list and the errors into another? Once separated, I'll be able to `bind_rows` into two dataframes, results and  errors. 

Off the top of my head, I can see how to do this with map, at least for the dataframes.

```{r}

# extract elements that are dataframes
playlist %>% 
  map(.f = function(x){
    if (is.data.frame(x)) return(x)
  }) %>% bind_rows()

```

So that seems to work and didn't take too much code. Good enough. (I checked, and the function defaults to returning `NULL` if the condition is not met.)

But applying the same logic to filtering the character strings out  

```{r}
# extract elements that are character strings
playlist %>% 
  map(.f = function(x){
    if (is.character(x)) return(x) 
  }) %>% as.character()

```

How to get rid of the `NULL` elements? I suppose I could do some base, but there's probably a nifty tidy way around this.

I suspect, however, that there is a better way to filter lists with `purrr::` combined with `dplyr::`. Possibly scary lambda functions? I need to level up my `purrr::`. 

## tweeps to the rescue

Thanks to James, Ken, and Francois, I found the `purrr::keep` function. Just what I wanted for Christmas! Cheers. 

<blockquote class="twitter-tweet" data-lang="en"><p lang="en" dir="ltr">Hey, purrr:: tweeps. Anyone know offhand about filtering a list by type? Here&#39;s a quick post outlining what I&#39;d like to do, and my hack. <a href="https://twitter.com/samclifford?ref_src=twsrc%5Etfw">@samclifford</a> <a href="https://twitter.com/rensa_co?ref_src=twsrc%5Etfw">@rensa_co</a>, perchance?  <a href="https://t.co/BxpXXfHUBc">https://t.co/BxpXXfHUBc</a></p>&mdash; Charles T. Gray (@cantabile) <a href="https://twitter.com/cantabile/status/1097716740627193856?ref_src=twsrc%5Etfw">February 19, 2019</a></blockquote>
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>


```{r}
playlist %>% keep(is.data.frame) %>% bind_rows()

playlist %>% keep(is.character) %>% as.character()
```

`w00t`

[^1]: I know, I know, I should find a more interesting  dataset than `iris`. 

