---
title: "does safely play nice with rma?"
description: |
  unpicking what happened with metafor::rma and purrr::safely
author:
  - name: Charles T. Gray
    url: https://twitter.com/cantabile
date: 02-25-2019
output:
  radix::radix_article:
    self_contained: false
categories:
  - error handling
  - debugging
  - metafor
  - purrr
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
# packages used in this post
library(tidyverse)
library(metasim)
library(metafor)
library(metabroom)

# for reproducibility
set.seed(38)
```

## lm

```{r lm data}
x <- seq(0, 10)

# simulate some data
(lm_data <- x %>% {
  tibble(
    x = .,
    y = rnorm(length(.), mean = 1.2 * ., sd = 2)
  )
})

# and take a look
lm_data %>% 
  ggplot(aes(x  = x, y = y)) +
  geom_smooth(method = "lm", 
              colour = "darkgrey",
              linetype = "dotted") +
  geom_point() 



```

Now, I expect to see the same results if I fit a linear model using the `lm` function. First, let's see what I can get out with pluck.

```{r}
# create safe version of lm
safe_lm <- safely(lm, otherwise = "lm model didn't work", quiet = FALSE)

# model data with lm and safely
lm_model <- lm_data %>% lm(y ~ x, data = .) 

safe_lm_model <- lm_data %>% safe_lm(y ~ x, data = .) 

# lm model results
lm_model %>% str(0)

# safe lm model results, same but in list with errors
safe_lm_model %>% str(1)


```

## rma

So, that all seemed cromulent enough, and just as the `log` example from the documentation had me following along. 

Now to try with `metafor::rma`.

```{r meta-analysis data}
# simulate meta-analysis data
rma_data <- sim_n(k = 7) %>% 
  sim_stats(wide = TRUE) %>% 
   escalc(
     data = .,
     measure = "SMD",
     m1i = mean_c,
     m2i = mean_i,
     sd1i = sd_c,
     sd2i = sd_i,
     n1i = n_c,
     n2i = n_i
   ) 

# peek at the data
rma_data %>% str(0)

# rma model works fine
rma_model <- rma_data %>% 
    rma(yi = yi, vi = vi, data = ., slab = study)

# take a look at results
rma_model %>% metabroom::tidy()

# plot data
rma_model %>% forest()



 
```

## error 

```{r eval=FALSE}
# set up safely function
safe_rma <- safely(rma, 
                   otherwise = "rma model didn't work", 
                   quiet = FALSE)
# 
# safe_rma_model <- rma_data %>% 
#     safe_rma(yi = yi, vi = vi, data = ., slab = study)
# 
# 
# # plot data
# safe_rma_model %>% forest()

```

Trying wrap `metafor::rma` with `purrr::safely` results in the following error:

```{}
Error: Can't convert a `rma.uni/rma` object to function
```

So, I have convinced myself, now. For some reason, `purrr::safely` does not play nicely with `metafor::rma`.

## what to do instead?

I suspect I'll need to do something with `tryCatch`. However, I think I'm ready to dive into James' [collateral](@goldie_collateral:_2018) package.  
