---
title: "a minimal radix workflow" 
description: |
  Plan is to write about setting up a radix:: thesis.
draft: true
author:
  - name: Charles T. Gray
    author_url: https://twitter.com/cantabile
date: 11-09-2018
output:
  radix::radix_article:
    self_contained: false
categories:
  - teaching
  - radix
  - thesis
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

I often get asked for R tips, and I feel like I disappoint when I say the thing that propels me along the most is saying how do I do this thing in an R way. I'm also super lazy, so I like to automate what I can along the way. 

I began using R in a biomedical research institute and was basted in the horrors of `aggregate` and `stringsAsFactors`. When I returned to R, having taken a break to frolic (yes, frolic).   

It's natural that I'm building my thesis in [`radix::`](https://rstudio.github.io/radix/), self-described in every new `radix` article, 

> Radix is a publication format for scientific and technical writing, native to the web. 

## barebones `radix`

> Shameless homage to Alison's [awesome post](https://alison.rbind.io/post/up-and-running-with-blogdown/#in-github).

### create a `radix` site

#### install `radix` and create project

To use `radix`, I had to upgrade to a [preview version](https://www.rstudio.com/products/rstudio/download/preview/) of RStudio.

Once you've installed `radix`,

```{r eval=FALSE, echo=TRUE}
devtools::install_github("rstudio/radix")
```

you can create website project,

**File >> New Project >> New Directory >> Radix Website**

#### get it on github

#### deploy via netlify

#### custom domain

### notes

- `.bib` is what's on [this](https://rstudio.github.io/radix/citations.html) page. 



*This page is a in progress.* 
