---
title: "collateral"
description: |
  catching non-convergent models
author:
  - name: Charles T. Gray
    url: {}
date: 01-05-2019
output:
  radix::radix_article:
    self_contained: false
categories:
 - error handling
bibliography: ../../biblio.bib
draft: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r packages}
# packages
library(tidyverse)
library(collateral)

here::here()
```

I'm writing simulations at the moment, and sometimes the meta-analysis algorithm fails due to some kind of non-convergence. I think. I'd like to understand that better some time. 

I think the collateral[@goldie_collateral:_2018] package might be the solution to my problem. 

I never did master this `tryCatch`[^1] business in the first place. So, at least there's nothing to unlearn. 

This post is a deep dive to see whether `collateral` can solve my problem and what else I'll learn along the way. 

I'll start with the [vignette](https://rensa.co/collateral/articles/collateral.html). 

[^1]: Is there a function to source the url of a function's documentation?





